Abstract Data Type Inference

### 2015-03-17 matching.tex
Outline of matching scheme inference.

>>>>

$\textsc{IsMatch}_{e,O}$:
\begin{align*}
  \bigvee_{o_1 \in O} \bigwedge_{o_2 \in O}
  \mathsf{g}(P(e,o_1), P(e,o_2), Q(e,o_1,o_2))
\end{align*}
represents whether $O$ is a match of $e$ according to the simple matching
scheme generated by $\mathsf{g}$, and
\begin{align*}
  \bigwedge_{\tup{e,O}\in \_} \lnot \textsc{IsMatch}_{e,O}
\end{align*}
insists that for any execution $e \in \mathcal{I}$ whose projection to
operations not in $O$ is not in $\mathcal{I}$, then $O$ must not be a match.

ENUMERATE LOTS OF EXECUTION PAIRS $\tup{e,e'}$ FOR WHICH $e'$ IS A PROJECTION
OF $e'$ WITH $e \in \mathcal{I}$ AND $e' \not\in \mathcal{I}$, AND LET $O$ BE
THE OPERATIONS IN $e$ BUT NOT $e'$. HOPEFULLY IF THIS FORMULA IS SATISFIABLE, A
MODEL FOR {\sf g} CAN BE A GOOD SIMPLE MATCHING SCHEME
